Colonies - Compute Continuums across Platforms

### 2023-04-04 paper_2023/paper.tex
wip

To address the aforementioned challenges, the paper introduces a framework termed Colonies which is available as open-source\footnote{https://github.com/colonyos/colonies} and designed to facilitate execution of computational workloads across a diverse range of platforms. Colonies is founded upon a loosely-coupled microservice architecture that beaks down complex workflows into composable functions. With the use of an HTTP protocol, these composable functions can be implemented in any computer language and be executed by independent executors deployed across various systems, e.g. cloud, edge, devices, or even in web browsers. Colonies orchestrates the execution and by using a zereo-trust security protocol, a collection of distributed executors can function as a single cohesive unit, thereby establishing seamless compute continuums across multiple platforms.

@@

In summary, Colonies is a highly versatile and scalable framework that can streamline the development and deployment of computational workloads across heterogeneous platforms while also ensuring full traceability and zero-trust security.
\end{abstract}

@@

Taking an AI model into production requires substantial software engineering expertise. In contrast to traditional IT workloads, both the data and the model must be managed in addition to the software itself. As most models require regular re-training or re-calibration, it must be possible to update deployed models and software seamlessly without losing information or breaking the system. In many cases, there is a constant flow of data ingested into the system which must be managed even in case of failures. This becomes even more challenging when nodes or parts of the underlying infrastructure become unavailable due to maintenance such as software updates, hardware replacements and sometimes missconfiguration failures.

@@

This paper presents a framework called Colonies, which is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The main objective is to create a tool where monolithic workflows can be broken down into independent and separated compute units that can be dynamically added or removed while executing workflows. These compute units can be implemented in any computer language and be deployed anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems.

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings with numerous approaches proposed to address the challenges in this field. For example, Apache Airflow \cite{apache_airflow} is a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop software development kits (SDKs) in various programming languages. However, Apache Airflow does not realy on a queuing system. Instead, it must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka}, to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed without reconfiguring the workflow engine, effectively making it work like a grid computing platform.

@@

>>>>

To address the aforementioned challenges, the paper introduces a framework termed Colonies which is available as open-source\footnote{https://github.com/colonyos/colonies} and designed to facilitate execution of computational workloads across a diverse range of platforms. It can be used to implement grid-alike distributed virtual computer systems, and is founded upon a loosely-coupled microservice architecture that beaks down complex workflows into composable functions. With the use of an HTTP protocol, these composable functions can be implemented in any computer language and be executed by independent executors deployed across various systems, e.g. cloud, edge, devices, or even in web browsers. Colonies orchestrates the execution and by using a zereo-trust security protocol, a collection of distributed executors can function as a single cohesive unit, thereby establishing seamless compute continuums across multiple platforms.

@@

In summary, Colonies is a highly versatile and scalable framework that can streamline development and deployment of computational workloads across heterogeneous platforms while ensuring full traceability and zero-trust security.
\end{abstract}

@@

Taking an AI model into production requires substantial software engineering expertise. In contrast to traditional IT workloads, both the data and the model must be managed in addition to the software itself. As most models require regular re-training or re-calibration, it must be possible to update deployed models and software seamlessly without losing information or breaking the system. In many cases, there is a constant flow of data ingested into the system which must be managed even in case of failures. This becomes even more challenging when nodes or parts of the underlying infrastructure become unavailable due to maintenance such as software updates, hardware replacements and sometimes missconfiguration problems.

@@

This paper presents a framework called Colonies, specifically designed for implementing distributed virtual computer systems that facilitate integration with other systems. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment, offering a modern approach to grid computing. The main objective is to create a tool where monolithic workflows can be broken down into independent and separated compute units that can be dynamically added or removed while executing workflows. These compute units can be implemented in any computer language and easily integrated with other systems, and then be deployed anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems.

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings with numerous approaches proposed to address the challenges in this field. For example, Apache Airflow \cite{apache_airflow} is a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop software development kits (SDKs) in various programming languages. However, Apache Airflow does not realy on a queuing system. Instead, it must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka}, to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed without reconfiguring the workflow engine, effectively turning it to a grid computing platform.

@@

Grid computing is a distributed computing model that allows multiple computers, sometimes geographically distributed, to work together as a cohesive system to solve large-scale computational problems. It can be used to harness resources from numerous computers to solve complex tasks.
